HBCC - ACC - STG - FEATURECOUNTS - GRCh38 - CQN - Sparse Model

### 2020-01-06 cmc-rnaseq-de/HBCC_ACC-STG_FEATURECOUNTS_GRCh38_CQN_Sparse.Rmd
fix contrasts

p <- ggplot(plotdata, aes(x=PC1, y=PC2))
p <- p + geom_point(aes(shape=Dx.Tissue, size=ageOfDeath))
p <- p + theme_bw() %+replace% theme(legend.position="top") + facet_grid(.~Dx.Tissue, scales = 'free_y')
p
```

>>>>

p <- ggplot(plotdata, aes(x=PC1, y=PC2))
p <- p + geom_point(aes(shape=Tissue, size=ageOfDeath))
p <- p + theme_bw() + theme(legend.position="right") + facet_grid(Tissue~., scales = 'free_y')
p
```
